|

### 2019-11-19 analysis/paper/paper.Rmd
Add parameter combinations to summary TS plot

```{r summary-ts-plot, fig.cap = summary_ts_cap}
### Figure 6
summary_ts_cap <- paste(
  htmlfig(),
  "ED2 plot-level predictions of",
  "net primary productivity (NPP),",
  "total leaf area index (LAI),",
  "production efficiency (NPP / LAI)",
  "and effective number of PFTs (N~PFT,eff~)",
  "by model configuration.",
  "Effective number of PFTs was calculated as the inverse",
  "of the Simpson diversity index with proportions expressed as",
  "fraction of aboveground biomass.",
  "Black dot with error bars is the observed mean and min/max value."
  # TODO REF
)
fig("summary-ts-plot.png")
```

>>>>

```{r summary-ts-plot, fig.cap = summary_ts_cap}
### Figure 6
summary_ts_cap <- paste(
  htmlfig(),
  "ED2 plot-level predictions of",
  "net primary productivity (NPP),",
  "total leaf area index (LAI),",
  "production efficiency (NPP / LAI)",
  "and effective number of PFTs (N~PFT,eff~)",
  "by model configuration.",
  "Effective number of PFTs was calculated as the inverse",
  "of the Simpson diversity index with proportions expressed as",
  "fraction of aboveground biomass.",
  "Each black line represents the same set of parameters across all configurations,",
  "and corresponds to the letters in Figure 5.",
  "Black dot with error bars is the observed mean and min/max value."
  # TODO REF
)
fig("summary-ts-plot.png")
```
